%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\
%%%%%%%% BEGIN PREAMBLE %%%%%%%%\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

%%% package imports %%%
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{mathptmx}% http://ctan.org/pkg/mathptmx
\usepackage[english]{babel} % English language/hyphenation
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{hyperref}

%%% layout settings %%%
\geometry{left=0.7in, right=0.7in, top=20mm, bottom=20mm}
\pagenumbering{gobble}
\setlength\parindent{0pt}

%%% new commands & environments %%%
\newcommand{\I}{--}
\newenvironment{mycenter}[1][\topsep]
  {\setlength{\topsep}{#1}\par\kern\topsep\centering}% \begin{mycenter}[<len>]
  {\par\kern\topsep}% \end{mycenter}

\newcommand*{\email}[1]{%
  \normalsize\href{mailto:#1}{#1}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  /
%%%%%%%%% END PREAMBLE %%%%%%%%% /
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%/

\begin{document}

\begin{mycenter}
\textbf{\LARGE Lorenzo Meninato} \\
726 N. Uber St., Philadelphia, PA \\
(610) 390-2484 $\cdot$ \email{lorenzomeninato@gmail.com} $\cdot$ \href{https://github.com/lmeninato}{https://github.com/lmeninato}

\end{mycenter}

\begin{mycenter}[0pt]
\textsc{\textbf{EDUCATION}}
\end{mycenter}

\vspace{-3mm}
\rule{\textwidth}{0.4pt}

\textbf{Haverford College} \hfill  \textbf{Haverford, PA} \\
\textit{Bachelor of Arts in Economics} \hfill May 2018

\begin{itemize}[topsep=0pt,noitemsep]
    \item[\I] Concentration in Mathematical Economics
	\item[\I] \textit{Relevant Coursework}: Data Structures \& Algorithms, Supervised Machine Learning, Statistical Computing, Probability Theory, Real Analysis II, Modern Algebra, Multivariable Calculus, Linear Algebra, Advanced Microeconomics
	\item[\I] Bachelor's Thesis: \textit{\href{https://github.com/lmeninato/ECON396/blob/master/Lorenzo\%20Meninato\%20Thesis.pdf}{Monopolistic Screening in Ride-Pooling Platforms}}
	\item[\I] Honors: UPenn Young Scholar, Rutgers Young Scholar Program in Discrete Mathematics
\end{itemize}

\vspace{2mm}

\begin{mycenter}[0pt]
\textsc{\textbf{WORK EXPERIENCE}}
\end{mycenter}

\vspace{-3mm}
\rule{\textwidth}{0.4pt}

\textbf{Federal Reserve Bank of New York} \hfill \textbf{New York, NY} \\
\textit{Analyst, Trading Risk and Modelling} \hfill July 2018 -- Present
\begin{itemize}[topsep=0pt,noitemsep]
	\item[\I] Programmed a credit derivatives exposure model for Federal Reserve stress testing in R. Documented code and used Git for version control.
	\item[\I] Developed a user-friendly front-end to provide model interactivity and visualize market data. Allows users to quickly visualize time series in an in-memory database and produce model outputs for Federal Reserve stress testing scenarios. Utilized SQL database metadata to automatically update the user-interface. 
\end{itemize}

\textbf{Haverford College} \hfill \textbf{Haverford, PA}\\
\textit{Teaching Assistant, Economics Department}
\hfill Jan 2017 -- May 2018
\begin{itemize}[topsep=0pt,noitemsep]
  \item[\I] Teaching assistant for advanced economics courses (Mathematical Economics and Advanced Microeconomics). Grade assignments and exams. 
  \item[\I] Collected, compiled and analyzed data obtained from a Cornell U affiliated adoption data
archive, to assemble a structured dataset using STATA.
\end{itemize}

\vspace{1mm}

\textbf{Federal Reserve Bank of New York} \hfill \textbf{New York, NY} \\
\textit{Summer Analyst, Market Risk Team} \hfill June 2017 -- August 2017
\begin{itemize}[topsep=0pt,noitemsep]
	\item[\I] Summer Analyst in the Market Risk Team (Supervision Group), an onsite team of bank examiners and
market risk specialists. 
	\item[\I] Analyze a firm's transactions of OTC derivatives. Report and present
how the transactions are structured and quantitatively assess what market risks the firm faces throughout the term of the
transaction.
\end{itemize}

\textbf{Bryn Mawr Capital Management} \hfill \textbf{Bryn Mawr, PA} \\
\textit{Private Equity Intern, HLG Partners L.P.} \hfill May 2012 -- August 2016
\begin{itemize}[topsep=0pt,noitemsep]
	\item[\I] Built datasets of macroeconomic and financial data that were the foundation for
analyzing long-term macro investments and back-testing econometric models.
	\item[\I] Tailored datasets, models, and data visualizations to the specifications outlined by the CEO.

\end{itemize}

\vspace{2mm}

\begin{mycenter}[0pt]
\textsc{\textbf{PERSONAL}}
\end{mycenter}

\vspace{-3mm}
\rule{\textwidth}{0.4pt}

\vspace{1.5mm}

\begin{tabularx}{\linewidth}{ll}

\hspace{-3mm}

\textbf{Skills}: & Linux, macOS, Windows \\
  & Proficient in R (shiny, tidyverse, devtools), Python (selenium, numpy, pandas), SQL, Git, and \LaTeX \\
  & Previous experience with q (kdb+), C++, MATLAB\\[1mm]

\hspace{-3mm}
\textbf{Languages}: & English, Spanish (fluent), French (proficient) \\
[1mm]



\hspace{-3mm}
\textbf{Interests}: & Soccer ; Haverford College Rowing Team (Captain) ; Haverford International Relations Society \\ [1mm]


\end{tabularx}

\end{document}
